---
title: "psych251.reproducibility.analysis.stress-heart rate coherence"
author: "Kris Evans"
date: "11/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Packages
```{r message=FALSE}
library(readr)
library(tidyverse)
library(knitr)
library(lme4)

```

### Read in processed data files 
Files generated in Prep_Coherence_MIDUSII.R script

```{r read in data}

setwd("~/R Mac working folder")

#load cleaned and merged data so farfrom this step and work from here - should have all the proper variables and merged diff data sets by M2ID
#should look wide and long data?

psych_251_repro_df <- read_csv("R Mac working folder/sommerfeldt2019/psych.251.repro.df.csv")

df <- psych_251_repro_df

```

```{r}
glimpse(df)


df %>% count(stress1)

```



```{r drop participants}
#drop participants from dataset who do not have stress and hr data timepoints minus stress/hr 6
#make stress and heart rate correlations

#drop stress - in paper mentioned only without five complete data points for sr stress but should also befor hr
df.s <- df %>% group_by(M2ID) %>% drop_na(stress1, stress2, stress3, stress4, stress5) %>% select(-stress6) 

#drophr framework but will keep HR in as isnt explicitly mentioned also some data spots arent good due to instrument rill return
df.shr <- df.s %>% group_by(M2ID) %>% drop_na(hr1, hr2, hr3, hr4, hr5) %>% select(-hr6)

#looks like 967 observations less than intended
summary(df.shr$IL6)

summary(df.shr$stress1)
summary(df.shr$stress2)
sd(df.shr$stress1)
sd(df.shr$stress2)


summarize(df.shr)



```
```{r}
 
```


```{r rename}

#rename var to separate easier
 df.shr1 <- rename(df.shr, stress_1 = stress1)
 
df.shr2 <- rename(df.shr1, stress_2 = stress2)
df.shr3 <- rename(df.shr2, stress_3 = stress3)  
df.shr4 <- rename(df.shr3, stress_4 = stress4)  
df.shr5 <- rename(df.shr4, stress_5 = stress5)  

df.shr6 <- rename(df.shr5, hr_1 = hr1) 
df.shr7 <- rename(df.shr6, hr_2 = hr2) 
df.shr8 <- rename(df.shr7, hr_3 = hr3) 
df.shr9 <- rename(df.shr8, hr_4 = hr4) 
df.shr10 <- rename(df.shr9, hr_5 = hr5) 
```

```{r pivot longer}
wDF <- df.shr10

#pivot longer, each participant has 5 rows per stress or hr

df.Ls <- pivot_longer(df.shr10, cols = starts_with("stress"), names_to = c("stress","timepoint"), names_sep = "_", values_to = "stress_value")  
 
  
df.Lhr <- pivot_longer(df.shr10, cols = starts_with("hr"), names_to = c("hr", "timepoint"), names_sep = "_", values_to = "hr_value")
```

```{r merge data sets and final}
#merge two long frames by tp and m2id

m.LDF <- merge(df.Ls, df.Lhr, 
                   by.x = c("M2ID", "timepoint"), 
                   by.y = c("M2ID", "timepoint"), 
                   all.x = TRUE, all.y = FALSE)

#select key variables needed for long dataframe
f.Ldf <- m.LDF %>% select(M2ID, timepoint, stress_value, hr_value, pwb2.x, COPE_denial.x, IL6.x, CRP.x, P4_CESD.x, P4_STAItrait.x, M2FAMNUM.x, P4_age.x)

#key variables for wide df

f.Wdf <- wDF %>% select(M2ID, pwb2, COPE_denial, IL6, CRP, P4_CESD, P4_STAItrait, M2FAMNUM, stress_1, stress_2, stress_3, stress_4, stress_5, hr_1, hr_2, hr_3, hr_4, hr_5, P4_age)
```

#See Prep_Coherence_MIDUSII.R for correlation computation. There, each subject’s set of heart rate and stress measures are subset to their #own data frame and a correlation is computed. The resulting within-subject (i.e., single-subject) r’s compose a new variable in the main #dataframe. ### Center correlations variable



```{r make coherence variable}
#cor between stress and hr within participant, unique for each participant coherence between variables -- dont think it is just at time points but an overall coefficient between stress and hr - return to this for supplemental time



```


##final wrangling and transforming
### Cluster mean center talked about for each variable to enable better comparison
#has to do with doing fixed effects models and havving effective predictor variables
#centers mean at 0, changes associations of variables- confusing, should try all variables in models
#especialy in multilevel models
#problemmatic if done for DV because reduces error term messes up std errors - never center DV (HR)
#helps get within and between effects equires different levels in model
#changes interecpt of regression model not the coeffcients-estimate withineffect cange at individual level for individual outcomes

```{r cluster_mean_center}
f.Ldf$stress_CMC = f.Ldf$stress_value - ave(f.Ldf$stress_value, f.Ldf$M2ID, na.rm=T)
f.Ldf$hr_CMC = f.Ldf$hr - ave(f.Ldf$hr, f.Ldf$M2ID, na.rm=T) #be aware if using thing can also CMC other predictors

f.Ldf$pwb2_CMC = f.Ldf$pwb2.x - ave(f.Ldf$pwb2.x, f.Ldf$M2ID, na.rm=T)
f.Ldf$P4_CESD_CMC = f.Ldf$P4_CESD.x - ave(f.Ldf$P4_CESD.x, f.Ldf$M2ID, na.rm=T)
f.Ldf$COPE_d_CMC = f.Ldf$COPE_denial.x - ave(f.Ldf$COPE_denial.x, f.Ldf$M2ID, na.rm=T)
f.Ldf$IL6_CMC = f.Ldf$IL6.x - ave(f.Ldf$IL6.x, f.Ldf$M2ID, na.rm=T)
f.Ldf$CRP_CMC = f.Ldf$CRP.x - ave(f.Ldf$CRP.x, f.Ldf$M2ID, na.rm=T)
f.Ldf$STAI_CMC = f.Ldf$P4_STAItrait.x - ave(f.Ldf$P4_STAItrait.x, f.Ldf$M2ID, na.rm=T)

```


### Mean Center variables only - paper uses MC variables not all CMC
```{r mean_center - Long DF}
#age was used as COV
f.Ldf$P4_age_MC = f.Ldf$P4_age.x - mean(f.Ldf$P4_age.x, na.rm=T)

# Self reports
f.Ldf$pwb2_MC = f.Ldf$pwb2.x - mean(f.Ldf$pwb2.x, na.rm=T)
f.Ldf$P4_CESD_MC = f.Ldf$P4_CESD.x - mean(f.Ldf$P4_CESD.x, na.rm=T)
f.Ldf$P4_STAItrait_MC = f.Ldf$P4_STAItrait.x - mean(f.Ldf$P4_STAItrait.x, na.rm=T)
f.Ldf$COPE_denial_MC = f.Ldf$COPE_denial.x - mean(f.Ldf$COPE_denial.x, na.rm=T)

# Divide pwb, cesd, stai by 10 so SEs larger, more interpretable
f.Ldf$pwb2_MC_d10 = f.Ldf$pwb2_MC/10.0
f.Ldf$P4_CESD_MC_d10 = f.Ldf$P4_CESD_MC/10.0
f.Ldf$P4_STAItrait_MC_d10 = f.Ldf$P4_STAItrait_MC/10.0

# Inflammatory
f.Ldf$IL6_MC = f.Ldf$IL6.x - mean(f.Ldf$IL6.x, na.rm=T)
f.Ldf$CRP_MC = f.Ldf$CRP.x - mean(f.Ldf$CRP.x, na.rm=T)
```

```{r Mean Center Wide DF}
# Wide data frame  f.WDF
f.Wdf$P4_age_MC = f.Wdf$P4_age - mean(f.Wdf$P4_age, na.rm=T)
# Self reports
f.Wdf$pwb2_MC = f.Wdf$pwb2 - mean(f.Wdf$pwb2, na.rm=T)
f.Wdf$P4_CESD_MC = f.Wdf$P4_CESD - mean(f.Wdf$P4_CESD, na.rm=T)
f.Wdf$P4_STAItrait_MC = f.Wdf$P4_STAItrait - mean(f.Wdf$P4_STAItrait, na.rm=T)
f.Wdf$COPE_denial_MC = f.Wdf$COPE_denial - mean(f.Wdf$COPE_denial, na.rm=T)
# Inflammatory
f.Wdf$IL6_MC = f.Wdf$IL6 - mean(f.Wdf$IL6, na.rm=T)
f.Wdf$CRP_MC = f.Wdf$CRP - mean(f.Wdf$CRP, na.rm=T)

```

### Log transform inflammatory markers for normal distribution 
```{r logtransform_IL6 and CRP}
f.Ldf$IL6_T = log2(f.Ldf$IL6.x)
f.Wdf$IL6_T = log2(f.Wdf$IL6)

f.Ldf$CRP_T = log(f.Ldf$CRP.x, base=10)
f.Wdf$CRP_T = log(f.Wdf$CRP, base=10)


##mean center variable from transform
f.Ldf$IL6_T_MC = f.Ldf$IL6_T - mean(f.Ldf$IL6_T, na.rm=T)
f.Ldf$CRP_T_MC = f.Ldf$CRP_T - mean(f.Ldf$CRP_T, na.rm=T)
```

```{r}
#save final df before tests

#saveoutput data framework to easily retrieve 
write.csv(f.Ldf,"psych.251.repro.f.Ldf.analysis.csv")
write.csv(f.Wdf,"psych.251.repro.w.Ldf.analysis.csv")

```


### Summary statistics and demographics

```{r summary stats if want to do more}
summary(wDF$P1_race)

wDF$race = as.factor(wDF$P1_race)

summary(wDF$race)
summary(as.factor(wDF$P1_sex))


hist(f.Ldf$stress_CMC)
hist(f.Ldf$IL6_T)
hist(f.Ldf$CRP_T)

```

# TESTS

## Stress-heart rate coherence associations

### PWB
```{r coherence_pwb}

# Run the test 

lmerM.pwb <- lmer(hr_value ~ stress_CMC * pwb2_MC_d10 + P4_age_MC*stress_CMC + (1 + stress_CMC|M2ID) + (1|M2FAMNUM.x), data = f.Ldf)
a.pwb <- anova(lmerM.pwb, type=3, test="F")
a.pwb
summary(lmerM.pwb)

  
```

### Depression
```{r coherence_depression}

# Run the test
lmerM = lmer(hr ~ stress_CMC * P4_CESD_C_d10 + P4_age_C*stress_CMC + (1 + stress_CMC|M2ID) + (1|M2FAMNUM), data=dfLs)
a = Anova(lmerM, type=3, test="F")
a
summary(lmerM)
   
```

### Anxiety
```{r coherence_anxiety}
# Run the test
lmerM = lmer(hr ~ stress_CMC * P4_STAItrait_C_d10 + P4_age_C*stress_CMC + (1 + stress_CMC|M2ID) + (1|M2FAMNUM), data=dfLs)
a = Anova(lmerM, type=3, test="F")
a
summary(lmerM)
   
```

### IL6
```{r coherence_IL6}

# Run the test
lmerM = lmer(hr ~ stress_CMC * IL6_T_C + P4_age_C*stress_CMC + (1 + stress_CMC|M2ID) + (1|M2FAMNUM), data=dfLs)
a = Anova(lmerM, type=3, test="F")
a
summary(lmerM)
  
```

### CRP
```{r coherence_CRP}

# Run the test
lmerM = lmer(hr ~ stress_CMC * CRP_T_C + P4_age_C*stress_CMC + (1 + stress_CMC|M2ID) + (1|M2FAMNUM), data=dfLs)
a = Anova(lmerM, type=3, test="F")
a
summary(lmerM)
  
```

### Denial
```{r denial}

# Run the test 
lmerM = lmer(hr ~ stress_CMC * COPE_denial_C + P4_age_C*stress_CMC + (1+ stress_CMC|M2ID) + (1|M2FAMNUM), data=dfLs)
a = Anova(lmerM, type=3, test="F")
a
summary(lmerM)
 
```

## Multiple Comparisons Correction
Holm-Bonferonni
```{r multiple_comparisons}
## p value for each test of a well-being marker
p = c(2.99E-07, 2.06E-09, 1.70E-08, 2.91E-06, 0.00762, 6.18E-06)
## Holm-bonferonni
p.adjust(p, method= 'holm')
# 
```



## FIGURE 1: Stress and heart rate by phase histograms

Facet-wrapped histograms of stress and heart rate at each phase of stress induction

```{r stress_by_phase_histograms, fig.width=8, fig.height=3, comment='#'}
ylimits = c(0, 610)
stressHist=ggplot()+
geom_histogram(data=f.Ldf, aes(stress_value), fill="green", binwidth=1, color="black") +
facet_wrap(~timepoint, ncol=5) +
labs(x="Self-reported stress", y="Number of subjects") +
ylim(ylimits)+
scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8,9,10) )+
theme_bw(base_size=18)
stressHist
```

```{r hr_by_phase_histograms, fig.width=8, fig.height=3, comment='#'}
xlimits = c(30,150)
ylimits = c(0, 240)
hrHist=ggplot()+
geom_histogram(data=f.Ldf, aes(hr_value), fill="red", binwidth=6, color="black") +
facet_wrap(~timepoint, ncol=5) +
labs(x="Heart rate", y="Number of subjects") +
ylim(ylimits)+
xlim(xlimits)+
geom_vline(xintercept=75, size=.5, color="blue")+
theme_bw(base_size=18)
hrHist
```
